A secondary screen architecture to accurately capture TV viewer interactions for content personalization in TV environments

### 2014-05-02 src/paper.tex
WIP: architecture

>>>>

This architecture consists of a secondary screen device (which might be implemented in personal devices such as smartphones and tablets) a set-top box (STB) with return channel, and a content provider (which is responsible for providing the interactive applications and for storing the data that was captured from viewers).

The secondary screen is used to identify the users that are present in the environment. That is, the viewer can authenticate to the local set-top box by using a transparent authentication mechanism. Thus, every time a viewer is nearby the STB using a a TV application with its

The second screen devices are Internet capable devices, which have TV related applications. The viewers use these applications to interact with the TV by evaluating, commenting or sharing TV content.

The STB is synchronized with the TV in order to contextualize the data that is captured.
\cite{Lee2010}
